Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-15 article.qmd
Run pre-commit on all files
Remove SBML downloading message from pooch
Add missing dot

One limitation of these tools is that they are not extensible from Python,
as they are not fully Python packages
but wrap libraries in other languages to do the simulation.
While they enable model definition and simulation control via Python scripts,
they don't fully leverage Python's extensive package ecosystem.
For example, in COPASI, users are restricted to predefined distributions for Random Parameter Scans
and cannot utilize the diverse distributions available in `scipy.stats`
Similarly, Tellurium doesn’t allow the use of Python solvers,
as adding new integrators requires C++ implementation.

@@

>>>>

One limitation of these tools is that they are not extensible from Python,
as they are not fully Python packages
but wrap libraries in other languages to do the simulation.
While they enable model definition and simulation control via Python scripts,
they don't fully leverage Python's extensive package ecosystem.
For example, in COPASI, users are restricted to predefined distributions for Random Parameter Scans
and cannot utilize the diverse distributions available in `scipy.stats`.
Similarly, Tellurium doesn’t allow the use of Python solvers,
as adding new integrators requires C++ implementation.

@@

```{python}
# | echo: false
# Pre-download SBML file, which is saved to a cache.
# Avoids printing the "downloading" message
from simbio.io import biomodels, sbml

sbml.load("repressilator.sbml")
```
